\subsection{List of Innovations}
\bit
\item Evaluate BP and Fast BP on many real world datasets.
\item Improve BP on Hadoop with convergence detection.
\item Use ECOC to extend Fast BP to multiclass.
\item Use quadratic approximation to extend Fast BP to multiclass.
\eit

\subsection{Labor Division}

The team will perform the following tasks
\bit
\item Implementation of BP on Hadoop with convergence detection [Yu Su,Huanchen Zhang,1 weeks]
\item Parse data and build network from datasets mentioned above [All, almost done]
\item Evaluate BP and Fast BP on large graphs [All, already have preliminary results, 1 week]
\item Research on extending Fast BP algorithm to Multiclass Problem [Guanyu Wang,Yuchen Tian, 2 weeks]
\item Implement and evaluate multiclass Fast BP algorithm [Yu Su,Huanchen Zhang,1 weeks]
\eit

\subsection{Activities}
\bit
\item Guanyu Wang: Performed dataset analysis and network building. Read papers and tried to deduct quadratic approximation for FaBP extension.
\item Yuchen Tian: Performed dataset analysis and network building. Proposed error correcting code methods for FaBP extension.
\item Yu Su: Performed dataset analysis and network building. Did some preliminary experiments.
\item Huanchen Zhang: Performed dataset analysis and network building. Did some preliminary experiments.
\eit

\subsection{Previous Labor Division}

The team will perform the following tasks
\bit
\item Implementation of BP on Hadoop [Yu Su,Huanchen Zhang,2 weeks]
\item Apply BP on Large Graph [All,2 weeks]
\item Research on extending Fast BP algorithm to Multiclass Problem [Guanyu Wang,Yuchen Tian,2 weeks]
\eit

